
Boston Dataset
==========================================================================
This is a problem from the Book *An Introduction to Statistical Learning,
with Applications in R, Springer* (<http://www-bcf.usc.edu/~gareth/ISL/>).
Chapter 3, exercise 15.

*This problem involves the Boston data set. We will now try to predict per
capita crime rate using the other cariables in this data set. In other words,
per capita crime rate is the response, and the other variables are the
predictor*

### Linear Regression

*For each predictor, fit a simple linear regression model to predict the
response. Describe your results. In which of the models is there a statistically
significant association between the predictor and the response? Create some
plots to back up your assertions*

```{r}
library(MASS)
library(ISLR)
library(ggplot2)
```

```{r}
# all the predictors except crim
vars <- names(Boston)
vars <- vars [vars != "crim"]

fits <- lapply(vars, function(x){
  formula <- paste("crim ~", x)
  fit <- lm (formula, data=Boston)
  list(name=x, fit=fit)
})


fits.pval <- lapply(fits, function(x){
  list ( name = x$name,
         pvalue = summary(x$fit)$coefficients[2,4])
})
```

```{r}
# place here the graphics comparing results
```